R Notebook

### 2017-05-11 manuscript/draft.Rmd
first go at data

>>>>

  Bird species richness was compiled from the Breeding Bird Survey (BBS) obtained using the Data Retriever software [@pardieck2017, @morris203]. The BBS data was initially filtered to exclude all aquatic species, unidentified species, and hybrids. All data from routes that did not meet BBS acceptable criteria were excluded. Only routes within the continental U.S.A were used so as to match the climatic dataset.
  Nineteen bioclimatic variables were derived from mean monthly temperature and precipitation from the 4km resolution PRISM dataset, allowing us to have yearly values for each variable [@prism]. This was subset to the eight variables identified by Harris [-@harris2015] to be non-correlated. For each BBS route the mean value for each variable within a 40km radius, equal to the length of a BBS route, was used to account for spatial heterogeneity. Satellite derived NDVI was from the NDIV3g dataset and was available from the time period 1981-2015 [@pinzon2014]. Elevation was from the SRTM 90m elevation dataset obtained using the R package raster [@hijmans2014, @jarvis2008].
  All models described below were fit using data from the years 1982-2003, and evaluated using data from the years 2004-2015. The year 1982 corresponds to the first complete year of NDVI observations. Only BBS routes with at least 25 yearly observations in the years 1982-2015 were used.
